\documentclass[11pt]{report}
\usepackage{enumitem}
\usepackage{float}
\usepackage[margin=50pt]{geometry}
\usepackage{hyperref}
\usepackage{unicode}

\pagestyle{empty}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}
\setlist[description]{leftmargin=*}
\setlist[itemize]{leftmargin=*}

% Job listing
\newenvironment{JobDescription}[4]{
    {\bf #1 } \hfill { #2}
    \\
    {\em #3 } \hfill {\em #4 }
    \begin{itemize}
} {
    \end{itemize}
}


\begin{document}
\begin{tabular}{@{}p{.65\textwidth}rp{.35\textwidth}}
    \bf{\LARGE{Andrey Turbov} \newline{\small{Sep 5, 1996}}} & & {\bf Contact} \\
    & {\small Phone:}       & {\small +7 (999) 215-6653} \\
    & {\small E-mail:}      & {\small unsip@tutamail.com} \\
    & {\small Github:}      & {\small \href{https://github.com/unsip}{https://github.com/unsip}} \\
    & {\small LinkedIn:}    & {\small \href{https://linkedin.com/in/andrey-turbov-8a6a91196}{Andrey Turbov}}
\end{tabular}

\vspace{10mm}
{\noindent I'm a software engineer with a few years of DevOps expertise.
    Self-education is of the highest value for me, which I'm always striving.
    Not only because regular studies got me into the industry, but also because
    I appreciate scientific endeavour and enjoy exploring world of abstract
    ideas. Hence, I'm looking forward to further improve my skills in software
    craftsmanship, giving my preference to interesting C++ projects. The
    essential job-aspect for me is to acquire expertise in solving challenging
    problems using modern technologies and practices. My experience in an
    international environment enables me to get along with foreign co-workers
    and customers quickly. In my spare time, I enjoy studying humanities,
    learning computer graphics, playing board games, and contemplating on
    aesthetically pleasing art.
}

\subsection*{Employment}
\begin{JobDescription}{T-Systems}{2020 --- present}{Software Developer}{St. Petersburg}
    \item Full stack maintainance and development of internal platform for executing and monitoring various bots
    \item Project architecture revision and design using UML diagrams
    \item Proposed solution prototyping along with introduction of Python RPC framework
    \item Held skill sharing meetings with colleagues
\end{JobDescription}

\begin{JobDescription}{}{2018 --- 2020}{Software Configuration Manager}{St. Petersburg}
    \item Regular presentations on international on-site meetings
    \item Implemented and maintained internal services and utilities such as:
    \begin{itemize}
        \item Custom dashboard web service for project environments
        \item Web service for generating delivery instructions for production OPS
        \item CLI utility for complex application configuration management
    \end{itemize}
    \item Designed and developed an orchestration solution using Puppet and Puppet Bolt
    \item Legacy CI/CD infrastucture maintainance and refactoring
    \item Support for international DEV, QA and production OPS teams
\end{JobDescription}

\subsection*{Education}
\begin{table}[H]
    \begin{tabular}{@{}p{0.20\textwidth}p{0.70\textwidth}}
        2014 --- 2016 & Saint Petersburg State University of Aerospace Instrumentation, Department of Computer Science \\
        2013 --- 2014 & Peter the Great Saint-Petersburg Polytechnic University, Department of Physics and Astronomy
    \end{tabular}
\end{table}

\goodbreak

\subsection*{Used Tools}
\begin{description}
    \item[Programming languages:]
    Python, C++(11/14/17), JavaScript (ES6)
    \item[Frameworks:]
    Django, Flask, ReactJS, RPyC
    \item[Development utilities:]
    Git, Bash, core *nix utilities
    \item[Operating systems:]
    Linux (RHEL, Debian, Arch, Gentoo)
    \item[Build systems and CI/CD:]
    Make, CMake, Gitlab CI, Jenkins
    \item[Containers/Virtualization:]
    Docker, Vagrant, VirtualBox
    \item[Infrastructure orchestration:]
    Ansible, Puppet, Bolt
    \item[Monitoring:]
    ELK stack, Grafana, Prometheus
    \item[Webservers:]
    Nginx, Apache
    \item[Databases:]
    PostgreSQL, OracleDB
\end{description}

\subsection*{Other}
\begin{description}
    \item[Languages:]
    English upper-intermediate, Russian native
    \item[Achievements:]
    participated in student physics and astronomy conferences/competitions,
    completed \href{https://gsl.mit.edu/}{MIT GSL} program at ITMO university
    \item[Hobbies:]
    \href{https://github.com/unsip}{programming}, philosophy, generative art, spider keeping
\end{description}

\end{document}
